### 2016-11-03 thesis/intro/intro.tex
tmp commit

% General intro to obesity.
% Implications of obesity -- disease associated with it and/or cancer.
Obesity has been one of the major global problems for more than a decade, associated with many noncommunicable diseases such as diabetes, cardiovascular diseases and certain types of cancers \citep{WHO2014}.
In fact, the risk of comorbidities increases with the increase in \gls{bmi}, where the risk becomes severe as the \gls{bmi} level approaches the obese category (citation from 2000 WHO).

The number of overweight and obese population, in both adults and children, have risen in every country of the world, and the trend continues as we speak.
Estimated to account for 3.4 million deaths per year and 93.6 million \glspl{daly} in 2010, obesity is a serious disease that continues to grow in our society (citation from 2010 WHO report needed).

@@

Obesity is defined as an abnormal or excessive fat accumulation that may impair health of that individual (citation).

@@

Obesity is caused by excessive intake of energy without expending the energy gained.
As one can suspect, there are many factors involved with the likelihood of an individual to become overweight and obese.

@@

There are many genetic evidence of obesity being caused by individual-level factors that makes some individuals more predisposed (right word??) to obesity than others (citation).
\textit{Talk about individual-level factors that affect obesity here (need citations on individual factors of obesity; e.g. genetic variation).}

@@

>>>>

% General intro to obesity.
% Implications of obesity -- disease associated with it and/or cancer.
Obesity has been one of the major global problems for more than a decade, associated with many noncommunicable diseases such as diabetes, cardiovascular diseases and certain types of cancers \citep{WHO2014}.
In fact, the risk of comorbidities increases with the increase in \gls{bmi}, where the risk becomes severe as the \gls{bmi} level approaches the obese category \citep{WHO2000}.

The number of overweight and obese population, in both adults and children, have risen in every country of the world, and the trend continues as we speak.
Estimated to account for 3.4 million deaths per year and 93.6 million \glspl{daly} in 2010, obesity is a serious disease that continues to grow in our society \citep{Lim2012}.

@@

Obesity is defined as an abnormal or excessive fat accumulation that may impair health of that individual \citep{Garrow1988}.

@@

Obesity is caused by continuous intake of excessive energy without expending the energy gained.
As one can suspect, there are many factors involved with the likelihood of an individual to become overweight and obese.

@@

There are many environmental factors associated with the global rise in obesity (discussed in \cref{ssub:Population-level_(macro-level)_factors}: \nameref{ssub:Population-level_(macro-level)_factors}).
Even though these environmental factors are probably the most significant contributor of global obesity epidemic, there are some individual-level, genetic factors that assist in the overall increase in the obese population.

There are many genetic evidence of obesity being caused by individual-level factors that makes some individuals more predisposed (right word??) to obesity than others (citation).

\citep{Neel1962}

LEP, LEPR, POMC, CART, MC4R, etc and its associated genetic/biological mechanisms\\

\citep{Montague1997}
\citep{Clement1998}
\citep{Jackson1997}
\citep{Krude1998}
\citep{Farooqi2003}
\citep{Kublaoui2006}
\citep{Dubern2001}
\citep{Challis2002}

FTO and other important GWAS studies \\

\citep{Frayling2007}
\citep{Dina2007}
\citep{Scuteri2007}
\citep{Gerken2007}

\textit{Talk about individual-level factors that affect obesity here (need citations on individual factors of obesity; e.g. genetic variation).}

@@

\citep{Calle2003}
